### 2022-04-27 inst/manuscript.Rmd
start to organize the manuscript as an package

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AMBIAGUA-2021-2823

In this repository, the code for the manuscript is available.

## Spatio-temporal variability of water quality in Billings Reservoir Central Body - São Paulo, Brazil

### Abstract

@@

## Variabilidade espaço-temporal da qualidade da água superficial do Corpo Central I da represa Billings - São Paulo, Brasil

### Resumo

>>>>

---
#title: ""
#author: ""
output: 
  bookdown::word_document2:
    reference_docx: template/word_template.docx
    number_sections: false
bibliography: [references/packages.bib, references/from-zotero.bib]
csl: template/abnt.csl
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
# knitr options
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
# Load the package
devtools::load_all()
```

```{r}
# sti_uni <- readr::read_rds("analises/resultados/sti_uni_tabela_arrumada.Rds")
```

# Spatio-temporal variability of water quality in Billings Reservoir Central Body - São Paulo, Brazil

**ABSTRACT**:

@@

**Variabilidade espaço-temporal da qualidade da água superficial do Corpo Central I da represa Billings - São Paulo, Brasil**

**RESUMO**:
